---
title: "How to use LandTrendR package"
output: rmarkdown::html_vignette
author: "Jorge Herrera"
date: "16 12 2021"
vignette: >
  %\VignetteIndexEntry{LandTrendR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title=FALSE)
```

## Package Configuration

This package requires configuration before going live. As it is based on the RGEE library it has a different environment configuration. The first step is to install the package:

```{r setup, eval=FALSE}
library(LandTrendR) #OPTIONAL
```

Before using it, a virtual environment must be generated for the python dependencies to work correctly. 

```{r virtualenv, eval=FALSE}
rgee::ee_install() # Install python environment required for GEE
```

If you have any problems, please clear the virtual environment cache of rgee with the following command 

```{r cleaning, eval=FALSE}
rgee::ee_clean_pyenv() # cleaning previous python environment (use it with precaution)
```

And restart the R version if the issue persists. 

Now, before jumping into LandTrendR, it is required one more step to prepared the environments to GEE. 

```{r init, eval=FALSE}
rgee::ee_Initialize() # Getting credentials from GEE to use their capabilities
```

## Getting started

### First Run - Default Parameters

```{r firstRun, eval=FALSE}
  LandTrendR::LtRun()
```


  
